---
title: "RESTAURANT DATA ANALYSIS -MONGODB"
output:
  
    html_document:
   
runtime: shiny
---

<br>

<p><h4><b>The data has been gathered from ZOMATO,a popular indian food delivery and restaurant aggregator.</b></h4></p>

>The below python script connects to the zomato API and loads upto a 100 restaurants details into the database at random.

```python
from pymongo import MongoClient
import requests
import random


client = MongoClient('mongodb+srv://admin:start123@cluster0.ss0ry.mongodb.net/test')
db=client['ZOMATO']
collection = db['RESTAURANT_INFO']

headers={"user_key": "78cf9c97da52bc00fb3733e09d50aa96", "Accept": "application/json"}  
id_list=random.sample(range(0,10000 ), 100)

for val in id_list:
    response = requests.get('https://developers.zomato.com/api/v2.1/restaurant?res_id='+str(val),headers=headers)
    if response.status_code == 200:
        collection.insert_one(response.json()).inserted_id
```
<br>

<p><h4><b>The API returns the details of each restaurant as a JSON (Javascript Object Notation) document,which we then store in mongodb</b></h4></p>

```
{
  "id": "16774318",
  "name": "Otto Enoteca & Pizzeria",
  "url": "https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village",
  "location": {
    "address": "1 5th Avenue, New York, NY 10003",
    "locality": "Greenwich Village",
    "city": "New York City",
    "latitude": "40.732013",
    "longitude": "-73.996155",
    "zipcode": "10003",
    "country_id": "216"
  },
  "average_cost_for_two": "60",
  "price_range": "2",
  "currency": "$",
  "thumb": "https://b.zmtcdn.com/data/pictures/chains/8/16774318/a54deb9e4dbb79dd7c8091b30c642077_featured_thumb.png",
  "featured_image": "https://d.zmtcdn.com/data/pictures/chains/8/16774318/a54deb9e4dbb79dd7c8091b30c642077_featured_v2.png",
  "photos_url": "https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/photos#tabtop",
  "menu_url": "https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/menu#tabtop",
  "events_url": "https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/events#tabtop",
  "user_rating": {
    "aggregate_rating": "3.7",
    "rating_text": "Very Good",
    "rating_color": "5BA829",
    "votes": "1046"
  },
  "has_online_delivery": "0",
  "is_delivering_now": "0",
  "has_table_booking": "0",
  "deeplink": "zomato://r/16774318",
  "cuisines": "Cafe",
  "all_reviews_count": "15",
  "photo_count": "18",
  "phone_numbers": "(212) 228-2930",
  
```


<br>

<p><h4><b>MongoDB is a document-oriented NoSQL database used for high volume data storage. Instead of using tables and rows as in the 
traditional relational databases, MongoDB makes use of collections and documents. Documents consist of key-value pairs which are the basic unit of data in MongoDB. 
Collections contain sets of documents and function which is the equivalent of relational database tables.</b></h4></p>

>Here we are using Mongodb's cloud database platform 
<a href="https://www.mongodb.com/cloud/atlas"> ATLAS</a> to
store the details of various restaurants.Each restaurant is a separae document in the database.

<br>
<br>
<h5><b> Loading Libraries</b><h5>
```{r message=FALSE, warning=FALSE}
library(mongolite)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(leaflet)
library(kableExtra)
library(shiny)
```

<br>
<h4><b>Connecting to the MONGODB CLOUD Database:</b></h4>
```{r}
Restaurants <- mongo("RESTAURANT_INFO",db='ZOMATO', url = "mongodb+srv://admin:start123@cluster0.ss0ry.mongodb.net/test")

```
<br>
<h4><b>Current number of records:</b></h4>
```{r}

Restaurants$count('{}')

```

<br>

<h4><b>Filtering relevant data:</b></h4>

```{r}

data <- Restaurants$find('{}')
data_filter<-data%>%select(R,id, name,location,average_cost_for_two,price_range,cuisines,opentable_support,user_rating,has_online_delivery,include_bogo_offers,is_table_reservation_supported,establishment)

```

<br>

<h4><b>We will include only those restaurants which have more than a 100 user ratings:</b></h4>


```{r}


  data_filter<-data_filter%>%filter(data_filter$user_rating$votes>100)


```

<br>

<h4><b>TYPE OF RESTAURANT VS USER_RATING</h4>
```{r}

frame1<-data.frame(as.data.frame(as.array(data_filter$establishment)),as.numeric(data_filter$user_rating$aggregate_rating))

names(frame1)=c('RESTAURANT_TYPE','USER_RATING')
frame1<-frame1%>%group_by(as.character(  RESTAURANT_TYPE))%>%summarise(avg_rating=round(mean(USER_RATING),1))%>%filter('as.character(RESTAURANT_TYPE)'!='character(0)')
names(frame1)=c('RESTAURANT_TYPE','USER_RATING')

frame1%>%ggplot(aes(x=RESTAURANT_TYPE,y=USER_RATING,fill=as.character(USER_RATING)))+geom_bar(stat = 'identity')+scale_fill_brewer(name = "Rating",palette = 'Reds')+theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

```

<br>
<h4><b>AVERAGE_COST_FOR_TWO vs TYPE OF RESTAURANT</b></h4>
```{r}
frame2<-data.frame(as.data.frame(as.array(data_filter$establishment)),(data_filter$average_cost_for_two))
names(frame2)=c('RESTAURANT_TYPE','AVERAGE_COST_FOR_TWO')

frame2<-frame2%>%group_by(as.character(  RESTAURANT_TYPE))%>%summarise(avg_cost_for_2=round(mean(AVERAGE_COST_FOR_TWO),1))%>%filter('as.character(RESTAURANT_TYPE)'!='character(0)')
names(frame2)=c('RESTAURANT_TYPE','AVERAGE_COST_FOR_TWO')

frame2%>%ggplot(aes(x=RESTAURANT_TYPE,y=AVERAGE_COST_FOR_TWO,fill=as.character(AVERAGE_COST_FOR_TWO)))+geom_bar(stat = 'identity')+scale_fill_brewer(name = "AVG_COST",palette = 'Reds')+theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```



<br>
<h4><b>CUISINE VS USER_RATING</b></h4>
```{r}
frame3<-data.frame(str_match(data_filter$cuisines,'^\\w+ \\w+|^\\w+'),(data_filter$user_rating$aggregate_rating))%>%arrange(desc(data_filter$user_rating$aggregate_rating))

names(frame3)=c('CUISINES','USER_RATING')

ggplot(data=frame3[1:6,],aes(x=CUISINES,y=USER_RATING))+geom_bar(stat = 'identity',aes(fill=CUISINES))+

scale_fill_brewer(palette = 'Reds')+theme_bw()

```


<br>
<h4><b>DOES HAVING ONLINE_DELIVERY IMPROVE USER_RATING</b></h4>
```{r}
frame4<-data.frame(data_filter$has_online_delivery,as.integer(data_filter$user_rating$aggregate_rating))


names(frame4)=c('ONLINE_DELIVERY','USER_RATING')

frame4<-frame4%>%group_by(as.character(ONLINE_DELIVERY))%>%summarise(avg_rating=mean(USER_RATING))
names(frame4)=c('ONLINE_DELIVERY','USER_RATING')

(frame4)%>%kbl()%>%kable_material_dark(c('striped','hover'))
```

<br>
<h4><b>PRICE_RANGE VS USER_RATING</b></h4>
```{r}
frame5<-data.frame(data_filter$price_range,as.integer(data_filter$user_rating$aggregate_rating))

names(frame5)=c('PRICE_RANGE','USER_RATING')

frame5<-frame5%>%group_by(as.character(PRICE_RANGE))%>%summarise(avg_rating=mean(USER_RATING))
names(frame5)=c('PRICE_RANGE','USER_RATING')

(frame5)%>%kbl()%>%kable_material_dark(c('striped','hover'))
```


<br>
<h4><b>WHERE ARE THE HIGHEST RATED RESTAURANTS LOCATED</b></h4>
```{r}
frame6<-data.frame(as.numeric(data_filter$location$latitude),as.numeric(data_filter$location$longitude),as.numeric(data_filter$user_rating$aggregate_rating))
names(frame6)=c('lat','lon','USER_RATING')


getColor <- function(frame6) {
  sapply(frame6$USER_RATING, function(USERRATING) {
  if(USERRATING > 4) {
    "green"
  } else if(USERRATING >=2&USERRATING <=4) {
    "orange"
  } else {
    "red"
  } })
}


icons <- awesomeIcons(
  icon = 'glyphicon glyphicon-glass',
  iconColor = 'black',
  library = 'glyphicon',
  markerColor = getColor(frame6)
)

 leaflet(data = frame6) %>%addTiles()%>%addAwesomeMarkers(~lon, ~lat,icon=icons,label = ~USER_RATING)
```



